---
title: "Sentiment Analysis"
author: "Amber Chin"
date: "3/1/2022"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

## Create heatmap with VADER scores

*VADER scores are obtained using the python file "vader_sentiment_analysis"*

Using the output dataframes from "vader_sentiment_analysis.ipynb", this code creates a heatmap of the average directional sentiment scores for each party.

```{r}
## load VADER scores from python output files
vader_same_party<- read_csv("bert_vader_same_scores.csv")
vader_same_party<- mutate(vader_same_party, type="same-party") 

vader_diff_party<- read_csv("bert_vader_diff_scores.csv")
vader_diff_party<- mutate(vader_diff_party, type="cross-party")

vader_total<- rbind(vader_same_party, vader_diff_party)
parties = c("Greens",'The Left','FDP','CDU','CSU','AfD','SPD') #remove independent/fraktionlos members
vader_total<- filter(vader_total, central_party %in% parties)
```

*Compare same-party vs cross-party VADER scores via "compound" score*

The "compound" score is a summary metric from the VADER model that measures the overall polarity of a text. We use this metric in each of the analyses for the sentiment score comparisons.
```{r}
## Welch t-test to compare sentiment scores
t.test(vader_diff_party$compound, vader_same_party$compound) 
```

```{r}
## get party-level sentiment score averages
party_avgs<- vader_total %>% 
  group_by(central_party,target_party, type) %>% 
  summarize(avg=round(mean(compound),digits=4)) %>% filter(target_party %in% parties)

## convert party names to German for consistency 
party_avgs$central_party[party_avgs$central_party=="Greens"] <- "Grünen"
party_avgs$target_party[party_avgs$target_party=="Greens"] <- "Grünen"
party_avgs$central_party[party_avgs$central_party=="The Left"] <- "Linke"
party_avgs$target_party[party_avgs$target_party=="The Left"] <- "Linke"

## generate plot
heatmap <- ggplot(party_avgs, aes(central_party, target_party)) +
  geom_tile(aes(fill = avg)) + 
  scale_fill_gradient(low = "red", high = "blue", limits=c(-0.4, 0.4), breaks=seq(-0.4,0.4,by=0.1)) + 
  xlab("Tweet Author Affiliation") +
  ylab("Recipient Affiliation ") +
  geom_text(aes(label = avg), color = "black", size = 4) +
  labs(fill="Average Sentiment Polarity") +
  theme(legend.direction = "vertical", legend.position = "right", 
        legend.title = element_blank(),
        legend.key.height = unit(2, 'cm'),
        axis.title= element_text(face= "bold", size=14),
        axis.text= element_text(size= 12)) +
  coord_fixed()
heatmap
```
