---
title: "ei_calculations"
author: "Amber Chin"
date: "5/12/2022"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(devtools)
library(igraph)
library(isnar)
```

## External-Internal Index Calculations

**Network-level calculations**

*Following-follower (ff) network EI values*
```{r}
## overall ff network EI values
ff_node<- read_csv("node_following-follower.csv") #node table for ff network
names(ff_node) <- c("id","label","party")

ff_edge<- read_csv("edge_following-follower.csv") #edge table for ff network
ff_edge<- ff_edge[,c(2,1,3)]

ff_net<- igraph::graph_from_data_frame(ff_edge, directed=T, vert=ff_node)
plot(ff_net, vertex.label = V(ff_net)$name)

ff_overall_ei_score = ei(ff_net, "party") #network-level EI Index
```

*Retweet (rt) network EI values*
```{r}
rt_node<- read_csv("node_retweets.csv") #node table for rt network
names(rt_node) <- c("id","label","party")

rt_edge<- read_csv("edge_retweets.csv") #edge table for rt network
rt_edge<- rt_edge[c('source','target','label','weight')]

rt_net<- igraph::graph_from_data_frame(rt_edge, directed=T, vert=rt_node)
plot(rt_net, vertex.label = V(rt_net)$name)

rt_overall_ei_score = ei(rt_net, "party") #network-level EI Index
```

*Mentions (mtn) network EI values*
```{r}
mtn_node<- read_csv("node_mentions.csv") #node table for mtn network

mtn_edge<- read_csv("edge_mentions.csv") #edge table for mtn network
mtn_edge<- mtn_edge[c('source','target','party','weight')]

mtn_net<- igraph::graph_from_data_frame(mtn_edge, directed=T, vert=mtn_node)
plot(mtn_net, vertex.label = V(mtn_net)$name)

mtn_overall_ei_score = ei(mtn_net, "party") #network-level EI Index
```

**Mentions Network: Party-level EI calculations**

*Die Linke*
```{r}
linke_node<- mtn_node
names(linke_node)<- c("source",'name','source_party')
linke_node<- merge(linke_node, mtn_edge, by = "source") #combine party info with MdB names

linke_edge<- linke_node %>% filter(source_party=="The Left") #get edges involving Die Linke
linke_edge<- linke_edge[,c(1,4:5)]

## filter necessary nodes from total node set
t1<- unique(linke_edge$source) #filter MdBs since not all are involved in this network
t2<- unique(linke_edge$target)
df<- as.data.frame(unique(c(t1,t2))) 
names(df)<- c('id')
linke_node<- rename(linke_node, "id"="source") 
linke_node<- merge(df, mtn_node, by = "id") #merge with MdB party data

## plot Die Linke network, EI Index calculation
l<- igraph::graph_from_data_frame(linke_edge, directed =T, vert=linke_node)
plot(l, vertex.label = V(l)$name)
linke_mtn = ei(l, "party")
```

*Die Gruenen*
```{r}
greens_node<- mtn_node
names(greens_node)<- c("source",'name','source_party')
greens_node<- merge(greens_node, mtn_edge, by = "source") #combine party info with MdB names

greens_edge<- greens_node %>% filter(source_party=="Greens") #get edges involving Die Linke
greens_edge<- greens_edge[,c(1,4:5)]

## filter necessary nodes from total node set
t1<- unique(greens_edge$source) #filter MdBs since not all are involved in this network
t2<- unique(greens_edge$target)
df<- as.data.frame(unique(c(t1,t2))) 
names(df)<- c('id')
greens_node<- rename(greens_node, "id"="source") 
greens_node<- merge(df, mtn_node, by = "id") #merge with MdB party data

## plot Die Gruenen network, EI Index calculation
g<- igraph::graph_from_data_frame(greens_edge, directed =T, vert=greens_node)
plot(g, vertex.label = V(g)$name)
greens_mtn = ei(g, "party")
```

*SPD*
```{r}
spd_node<- mtn_node
names(spd_node)<- c("source",'name','source_party')
spd_node<- merge(spd_node, mtn_edge, by = "source") #combine party info with MdB names

spd_edge<- spd_node %>% filter(source_party=="SPD") #get edges involving Die Linke
spd_edge<- spd_edge[,c(1,4:5)]

## filter necessary nodes from total node set
t1<- unique(spd_edge$source) #filter MdBs since not all are involved in this network
t2<- unique(spd_edge$target)
df<- as.data.frame(unique(c(t1,t2))) 
names(df)<- c('id')
spd_node<- rename(spd_node, "id"="source") 
spd_node<- merge(df, mtn_node, by = "id") #merge with MdB party data

## plot SPD network, EI Index calculation
s<- igraph::graph_from_data_frame(spd_edge, directed =T, vert=spd_node)
plot(s, vertex.label = V(s)$name)
spd_mtn = ei(s, "party")
```

*AfD*
```{r}
afd_node<- mtn_node
names(afd_node)<- c("source",'name','source_party')
afd_node<- merge(afd_node, mtn_edge, by = "source") #combine party info with MdB names

afd_edge<- afd_node %>% filter(source_party=="AfD") #get edges involving AfD
afd_edge<- afd_edge[,c(1,4:5)]

## filter necessary nodes from total node set
t1<- unique(afd_edge$source) #filter MdBs since not all are involved in this network
t2<- unique(afd_edge$target)
df<- as.data.frame(unique(c(t1,t2))) 
names(df)<- c('id')
afd_node<- rename(afd_node, "id"="source") 
afd_node<- merge(df, mtn_node, by = "id") #merge with MdB party data

## plot AfD network, EI Index calculation
a<- igraph::graph_from_data_frame(afd_edge, directed =T, vert=afd_node)
plot(a, vertex.label = V(a)$name)
afd_mtn = ei(a, "party")
```

*CDU/CSU*
```{r}
cdu_node<- mtn_node
names(cdu_node)<- c("source",'name','source_party')
cdu_node<- merge(cdu_node, mtn_edge, by = "source") #combine party info with MdB names

cdu_edge<- cdu_node %>% filter(source_party=="CDU"|source_party=="CSU") #get edges involving CDU/CSU
cdu_edge<- cdu_edge[,c(1,4:5)]

## filter necessary nodes from total node set
t1<- unique(cdu_edge$source) #filter MdBs since not all are involved in this network
t2<- unique(cdu_edge$target)
df<- as.data.frame(unique(c(t1,t2))) 
names(df)<- c('id')
cdu_node<- rename(cdu_node, "id"="source") 
cdu_node<- merge(df, mtn_node, by = "id") #merge with MdB party data

## plot CDU/CSU network, EI Index calculation
c<- igraph::graph_from_data_frame(cdu_edge, directed =T, vert=cdu_node)
plot(c, vertex.label = V(c)$name)
cducsu_mtn = ei(c, "party")
```

*FDP*
```{r}
fdp_node<- mtn_node
names(fdp_node)<- c("source",'name','source_party')
fdp_node<- merge(fdp_node, mtn_edge, by = "source") #combine party info with MdB names

fdp_edge<- fdp_node %>% filter(source_party=="FDP") #get edges involving FDP
fdp_edge<- fdp_edge[,c(1,4:5)]

## filter necessary nodes from total node set
t1<- unique(fdp_edge$source) #filter MdBs since not all are involved in this network
t2<- unique(fdp_edge$target)
df<- as.data.frame(unique(c(t1,t2))) 
names(df)<- c('id')
fdp_node<- rename(fdp_node, "id"="source") 
fdp_node<- merge(df, mtn_node, by = "id") #merge with MdB party data

## plot FDP network, EI Index calculation
f<- igraph::graph_from_data_frame(fdp_edge, directed =T, vert=fdp_node)
plot(f, vertex.label = V(f)$name)
fdp_mtn = ei(f, "party")
```

**Following-Follower Network: Party-level EI calculations**

*Die Linke*
```{r}
linke_node<- ff_node
names(linke_node)<- c("source",'name','source_party')
linke_node<- merge(linke_node, ff_edge, by = "source") #combine party info with MdB names
linke_node<- linke_node[,1:4]

linke_edge<- linke_node %>% filter(source_party=="The Left") #get edges involving Die Linke
linke_edge<- linke_edge[,c(1,4)]

## filter necessary nodes from total node set
t1<- unique(linke_edge$source) #filter MdBs since not all are involved in this network
t2<- unique(linke_edge$target)
df<- as.data.frame(unique(c(t1,t2))) 
names(df)<- c('id')
linke_node<- rename(linke_node, "id"="source") 
linke_node<- merge(df, ff_node, by = "id") #merge with MdB party data

## plot Die Linke network, EI Index calculation
l<- igraph::graph_from_data_frame(linke_edge, directed =T, vert=linke_node)
plot(l, vertex.label = V(l)$name)
linke_ff = ei(l, "party")
```

*Die Gruenen*
```{r}
greens_node<- ff_node
names(greens_node)<- c("source",'name','source_party')
greens_node<- merge(greens_node, ff_edge, by = "source") #combine party info with MdB names
greens_node<- greens_node[,1:4]

greens_edge<- greens_node %>% filter(source_party=="Greens") #get edges involving Greens
greens_edge<- greens_edge[,c(1,4)]

## filter necessary nodes from total node set
t1<- unique(greens_edge$source) #filter MdBs since not all are involved in this network
t2<- unique(greens_edge$target)
df<- as.data.frame(unique(c(t1,t2))) 
names(df)<- c('id')
greens_node<- rename(greens_node, "id"="source") 
greens_node<- merge(df, ff_node, by = "id") #merge with MdB party data

## plot Greens network, EI Index calculation
g<- igraph::graph_from_data_frame(greens_edge, directed =T, vert=greens_node)
plot(g, vertex.label = V(g)$name)
greens_ff = ei(g, "party")
```

*CDU/CSU*
```{r}
cdu_node<- ff_node
names(cdu_node)<- c("source",'name','source_party')
cdu_node<- merge(cdu_node, ff_edge, by = "source") #combine party info with MdB names
cdu_node<- cdu_node[,1:4]

cdu_edge<- cdu_node %>% filter(source_party=="CDU"|source_party=="CSU") #get edges involving CDU/CSU
cdu_edge<- cdu_edge[,c(1,4)]

## filter necessary nodes from total node set
t1<- unique(cdu_edge$source) #filter MdBs since not all are involved in this network
t2<- unique(cdu_edge$target)
df<- as.data.frame(unique(c(t1,t2))) 
names(df)<- c('id')
cdu_node<- rename(cdu_node, "id"="source") 
cdu_node<- merge(df, ff_node, by = "id") #merge with MdB party data

## plot CDU/CSU network, EI Index calculation
c<- igraph::graph_from_data_frame(cdu_edge, directed =T, vert=cdu_node)
plot(c, vertex.label = V(c)$name)
cducsu_ff = ei(c, "party")
```

*AfD*
```{r}
afd_node<- ff_node
names(afd_node)<- c("source",'name','source_party')
afd_node<- merge(afd_node, ff_edge, by = "source") #combine party info with MdB names
afd_node<- afd_node[,1:4]

afd_edge<- afd_node %>% filter(source_party=="AfD") #get edges involving AfD
afd_edge<- afd_edge[,c(1,4)]

## filter necessary nodes from total node set
t1<- unique(afd_edge$source) #filter MdBs since not all are involved in this network
t2<- unique(afd_edge$target)
df<- as.data.frame(unique(c(t1,t2))) 
names(df)<- c('id')
afd_node<- rename(afd_node, "id"="source") 
afd_node<- merge(df, ff_node, by = "id") #merge with MdB party data

## plot AfD network, EI Index calculation
a<- igraph::graph_from_data_frame(afd_edge, directed =T, vert=afd_node)
plot(a, vertex.label = V(a)$name)
afd_ff = ei(a, "party")
```

*SPD*
```{r}
spd_node<- ff_node
names(spd_node)<- c("source",'name','source_party')
spd_node<- merge(spd_node, ff_edge, by = "source") #combine party info with MdB names
spd_node<- spd_node[,1:4]

spd_edge<- spd_node %>% filter(source_party=="SPD") #get edges involving SPD
spd_edge<- spd_edge[,c(1,4)]

## filter necessary nodes from total node set
t1<- unique(spd_edge$source) #filter MdBs since not all are involved in this network
t2<- unique(spd_edge$target)
df<- as.data.frame(unique(c(t1,t2))) 
names(df)<- c('id')
spd_node<- rename(spd_node, "id"="source") 
spd_node<- merge(df, ff_node, by = "id") #merge with MdB party data

## plot SPD network, EI Index calculation
s<- igraph::graph_from_data_frame(spd_edge, directed =T, vert=spd_node)
plot(s, vertex.label = V(s)$name)
spd_ff = ei(s, "party")
```

*FDP*
```{r}
fdp_node<- ff_node
names(fdp_node)<- c("source",'name','source_party')
fdp_node<- merge(fdp_node, ff_edge, by = "source") #combine party info with MdB names
fdp_node<- fdp_node[,1:4]

fdp_edge<- fdp_node %>% filter(source_party=="FDP") #get edges involving FDP
fdp_edge<- fdp_edge[,c(1,4)]

## filter necessary nodes from total node set
t1<- unique(fdp_edge$source) #filter MdBs since not all are involved in this network
t2<- unique(fdp_edge$target)
df<- as.data.frame(unique(c(t1,t2))) 
names(df)<- c('id')
fdp_node<- rename(fdp_node, "id"="source") 
fdp_node<- merge(df, ff_node, by = "id") #merge with MdB party data

## plot FDP network, EI Index calculation
f<- igraph::graph_from_data_frame(fdp_edge, directed =T, vert=fdp_node)
plot(f, vertex.label = V(f)$name)
fdp_ff = ei(f, "party")
```

**Retweets Network: Party-level EI calculations**

*Die Linke*
```{r}
linke_node<- rt_node
names(linke_node)<- c("source",'name','source_party')
linke_node<- merge(linke_node, rt_edge, by = "source") #combine party info with MdB names

linke_edge<- linke_node %>% filter(source_party=="The Left") #get edges involving Die Linke
linke_edge<- linke_edge[,c(1,4:5)]

## filter necessary nodes from total node set
t1<- unique(linke_edge$source) #filter MdBs since not all are involved in this network
t2<- unique(linke_edge$target)
df<- as.data.frame(unique(c(t1,t2))) 
names(df)<- c('id')
linke_node<- rename(linke_node, "id"="source") 
linke_node<- merge(df, rt_node, by = "id") #merge with MdB party data

## plot Die Linke network, EI Index calculation
l<- igraph::graph_from_data_frame(linke_edge, directed =T, vert=linke_node)
plot(l, vertex.label = V(l)$name)
linke_rt = ei(l, "party")
```

*Die Gruenen*
```{r}
greens_node<- rt_node
names(greens_node)<- c("source",'name','source_party')
greens_node<- merge(greens_node, rt_edge, by = "source") #combine party info with MdB names

greens_edge<- greens_node %>% filter(source_party=="Greens") #get edges involving Greens
greens_edge<- greens_edge[,c(1,4:5)]

## filter necessary nodes from total node set
t1<- unique(greens_edge$source) #filter MdBs since not all are involved in this network
t2<- unique(greens_edge$target)
df<- as.data.frame(unique(c(t1,t2))) 
names(df)<- c('id')
greens_node<- rename(greens_node, "id"="source") 
greens_node<- merge(df, rt_node, by = "id") #merge with MdB party data

## plot Greens network, EI Index calculation
g<- igraph::graph_from_data_frame(greens_edge, directed =T, vert=greens_node)
plot(g, vertex.label = V(g)$name)
greens_rt = ei(g, "party")
```

*SPD*
```{r}
spd_node<- rt_node
names(spd_node)<- c("source",'name','source_party')
spd_node<- merge(spd_node, rt_edge, by = "source") #combine party info with MdB names

spd_edge<- spd_node %>% filter(source_party=="SPD") #get edges involving SPD
spd_edge<- spd_edge[,c(1,4:5)]

## filter necessary nodes from total node set
t1<- unique(spd_edge$source) #filter MdBs since not all are involved in this network
t2<- unique(spd_edge$target)
df<- as.data.frame(unique(c(t1,t2))) 
names(df)<- c('id')
spd_node<- rename(spd_node, "id"="source") 
spd_node<- merge(df, rt_node, by = "id") #merge with MdB party data

## plot SPD network, EI Index calculation
s<- igraph::graph_from_data_frame(spd_edge, directed =T, vert=spd_node)
plot(s, vertex.label = V(s)$name)
spd_rt = ei(s, "party")
```

*AfD*
```{r}
afd_node<- rt_node
names(afd_node)<- c("source",'name','source_party')
afd_node<- merge(afd_node, rt_edge, by = "source") #combine party info with MdB names

afd_edge<- afd_node %>% filter(source_party=="AfD") #get edges involving AfD
afd_edge<- afd_edge[,c(1,4:5)]

## filter necessary nodes from total node set
t1<- unique(afd_edge$source) #filter MdBs since not all are involved in this network
t2<- unique(afd_edge$target)
df<- as.data.frame(unique(c(t1,t2))) 
names(df)<- c('id')
afd_node<- rename(afd_node, "id"="source") 
afd_node<- merge(df, rt_node, by = "id") #merge with MdB party data

## plot AfD network, EI Index calculation
a<- igraph::graph_from_data_frame(afd_edge, directed =T, vert=afd_node)
plot(a, vertex.label = V(a)$name)
afd_rt = ei(a, "party")
```

*FDP*
```{r}
fdp_node<- rt_node
names(fdp_node)<- c("source",'name','source_party')
fdp_node<- merge(fdp_node, rt_edge, by = "source") #combine party info with MdB names

fdp_edge<- fdp_node %>% filter(source_party=="FDP") #get edges involving FDP
fdp_edge<- fdp_edge[,c(1,4:5)]

## filter necessary nodes from total node set
t1<- unique(fdp_edge$source) #filter MdBs since not all are involved in this network
t2<- unique(fdp_edge$target)
df<- as.data.frame(unique(c(t1,t2))) 
names(df)<- c('id')
fdp_node<- rename(fdp_node, "id"="source") 
fdp_node<- merge(df, rt_node, by = "id") #merge with MdB party data

## plot FDP network, EI Index calculation
f<- igraph::graph_from_data_frame(fdp_edge, directed =T, vert=fdp_node)
plot(f, vertex.label = V(f)$name)
fdp_rt = ei(f, "party")
```

*CDU/CSU*
```{r}
cdu_node<- rt_node
names(cdu_node)<- c("source",'name','source_party')
cdu_node<- merge(cdu_node, rt_edge, by = "source") #combine party info with MdB names

cdu_edge<- cdu_node %>% filter(source_party=="CDU"|source_party=="CSU") #get edges involving CDU/CSU
cdu_edge<- cdu_edge[,c(1,4:5)]

## filter necessary nodes from total node set
t1<- unique(cdu_edge$source) #filter MdBs since not all are involved in this network
t2<- unique(cdu_edge$target)
df<- as.data.frame(unique(c(t1,t2))) 
names(df)<- c('id')
cdu_node<- rename(cdu_node, "id"="source") 
cdu_node<- merge(df, rt_node, by = "id") #merge with MdB party data

## plot CDU/CSU network, EI Index calculation
c<- igraph::graph_from_data_frame(cdu_edge, directed =T, vert=cdu_node)
plot(c, vertex.label = V(c)$name)
cducsu_rt = ei(c, "party")
```

```{r}
## compile EI data
ei_index = c(greens_mtn,linke_mtn,cducsu_mtn,afd_mtn,spd_mtn,fdp_mtn,
             greens_rt,linke_rt,cducsu_rt,afd_rt,spd_rt,fdp_rt,
             greens_ff,linke_ff,cducsu_ff,afd_ff,spd_ff,fdp_ff)
party = c(rep(c("Grünen","Linke","CDU/CSU","AfD","SPD","FDP"),3))
network_type = c(rep("mentions",6), rep("retweet",6), rep("following-follower",6))
ei_df<- as.data.frame(cbind(ei_index,party,network_type))
ei_df$ei_index<- as.numeric(ei_df$ei_index)

## generate plot of EI values
dev.new(width=9, height=5)
ei_plot<- ggplot(data=ei_df, aes(x=party, y=ei_index, fill=network_type)) +
  geom_bar(stat="identity", width = 0.8, position=position_dodge()) +
  scale_y_continuous(limits=c(-1, 1.0), breaks=c(-1.5,-1,-0.5,0,0.5,1.0)) + 
  scale_fill_manual("Network Type", values = c("following-follower" ="orange", "mentions" ="purple", "retweet"="blue")) +
  xlab("Political Party") +
  ylab("E-I Index") +
  theme(axis.title = element_text(size = 18, face = "bold"),
        axis.text = element_text(size = 14, face = "bold"),
        legend.text = element_text(size = 14),
        legend.title = element_text(size=14, face="bold"),
        legend.position=c(.5,.9),
        legend.background = element_rect(size=0.5, linetype="solid", colour ="black"),
        legend.direction= "horizontal") +
  geom_hline(yintercept=0, linetype="dashed", color = "dark green") 
ei_plot
```
